Argennon: A Scalable Smart Contract Platform

### 2021-04-28 tex/sections/avm.tex
Update persistence section
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fix a typo
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon virtual machine does not have a fixed word size. Any instruction of the Argennon Virtual Machine has
its specific word size, and the addressable memory areas are byte addressable.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called a trie.}. The AVM has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by using one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree.(\texttt{|} is the concatenating operator.)

@@

All Argennon prefix trees have an equal branching factor \(\beta\). Therefore, we can represent an Argennon
prefix tree as a sequence of fractional numbers in base \(\beta\):
\[
    <A^{(1)},A^{(2)},A^{(3)},\dots>
\]
Where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)}<A^{(i+1)}\). A typical choice for \(\beta\)
could be \(2^8\).

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any data. Assume that we have a string of digits which are in base $\beta$, we
know that $k$ first digits belong to an Argennon's identifier, but we don't know the value of $k$.
Algorithm~\ref{alg:prefix_id} can extract the prefixed identifier uniquely. We can apply this algorithm
multiple times to a sequence to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

@@

The heap of the Argennon Virtual Machine is a persistent memory area which stores \emph{memory chunks}. A Memory
chunk is a byte addressable piece of memory which has a separate address space starting from 0. Each chunk has a
fixed size and different chunks need not be equally sized. Chunks are stored in the heap area and every chunk is
assigned a unique identifier: \texttt{chunkID}. As a result, the address of every memory location inside
the heap area can be considered as a pair: \texttt{(chunkID, offset)}.

@@

\note{For AVM smart contracts \emph{reentrancy} can only happen in read-only mode and is totally safe.
At the same time call-back patterns can be easily implemented by using \texttt{spawn} instruction.}

>>>>

The Argennon virtual machine does not have a fixed word size. Any instruction of the AVM has
its specific word size, and the addressable memory areas are byte addressable.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called a trie.}. The Argennon has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by using one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree.(\texttt{|} is the concatenating operator.)

@@

All Argennon prefix trees have an equal branching factor \(\beta\). Therefore, we can represent an Argennon
prefix tree as a sequence of fractional numbers in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)
\]
Where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)}<A^{(i+1)}\). A typical choice for \(\beta\)
could be \(2^8\).

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any sequence. Assume that we have a string of digits in base $\beta$, we
know that $k$ first digits belong to an Argennon's identifier, but we don't know the value of $k$.
Algorithm~\ref{alg:prefix_id} can be used to extract the prefixed identifier uniquely. Also, we can apply this algorithm
multiple times to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

@@

The heap of the Argennon Virtual Machine is a persistent memory area which stores \emph{memory chunks}. A Memory
chunk is a byte addressable piece of continuous memory which has a separate address space starting from 0. Each chunk
has a fixed size and different chunks need not be equally sized. Chunks are stored in the heap area and every chunk is
assigned a unique identifier: \texttt{chunkID}. As a result, the address of every memory location inside
the heap area can be considered as a pair: \texttt{(chunkID, offset)}.

@@

\note{For AVM smart contracts \emph{reentrancy} can only happen in read-only mode and is totally safe.
At the same time, call-back patterns can be easily implemented by using \texttt{spawn} instruction.}
